Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-30 analysis/paper/paper.qmd
Added codes for eco&forest zones

############ explore tcsa with MODERN eco_regions #####

@@

>>>>

############ explore tcsa with MODERN eco_regions #######

@@

############ explore tcsa with MODERN eco_regions & forest zones #######

veg_forest <- read_sf(here("analysis/data/gis_data/eco_forest_two.shp"))

veg_forest <- st_transform(veg_forest, crs = st_crs(4326))

ggplot() +
  geom_sf(data = veg_forest) +
  coord_sf()

pts_forest <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_forest))
ggplot() +
  geom_sf(data = pts_forest)

points_in_veg_zones_forest <- 
st_join(veg_forest, 
        pts_forest, 
        join = st_contains)

ggplot() +
  geom_sf(data = veg_forest, aes(fill = veg_forest$Zone)) + #add color for vegetation polygons
  geom_sf(data = pts_forest, aes(color = pts_forest$min_tcsa)) +
  theme_minimal()

ggplot(points_in_veg_zones_forest) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest))
